{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2022-01-07 main.tex
Some theory

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature. Classical statistical methods can often process this data, but only FDA allows extracting information given by the smoothness of the underlying process (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).\\
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}

	 \begin{equation}
	 	Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
	 	\qquad i = 1, ..., n
	 \end{equation}

@@

	\begin{equation}
		\int_{0}^{1} \lvert f \rvert^2 d\mu < \infty
	\end{equation}

@@

	\begin{equation}
		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 d\mu.
	\end{equation}

@@

	\subsection{Different Bases of $\mathbb{L}^2$}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	This, however, does not really yield a basis of $\mathbb{L}^2$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2$. To really obtain a basis of $\mathbb{L}^2$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made. As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2$ will serve as a sufficient approximation for an appropriately chosen B-spline basis. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

@@

@@

@@

	\begin{equation}
    	 Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}

@@

   \begin{equation}
	   c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,ds \ +\epsilon]
   \end{equation}

   \begin{equation}
 	  c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, ds \: | \: X]  + E[\epsilon |\mathbf{X}]
   \end{equation}

   \begin{equation}
      c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,ds
   \end{equation}

@@

    \begin{equation}
    	\int \beta(s)X(s) \,dt \ = \sum_{k=1}^{K} c_{k} \int B_{k}(t)X_{i}(t)\,dt =: \sum_{k=1}^{K} x_{ik} c_{k} 
    \end{equation}

@@

    \begin{equation}
    	f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}
    \end{equation}

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature. Classical statistical methods can often process this data, but only FDA allows extracting information given by the smoothness of the underlying process (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).\\
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:

	 \begin{equation}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., n
	 \end{equation}

@@

	\begin{equation}
		\int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

@@

	\begin{equation}
		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
	\end{equation}

@@

	\subsection{Bases of $\mathbb{L}^2$}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	This, however, does not really yield a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made. As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen B-spline basis. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	{\color{red} Write something about how to approximate functions by truncating the basis.}

	\begin{equation}
		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t) = \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t)
	\end{equation}

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} \psi_j Z_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}
    	 Y =  \int \beta(s)X(s) \,\mathrm{d}t \ +\epsilon
    \end{equation}

@@

   \begin{equation}
	   c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,\mathrm{d}s \ +\epsilon]
   \end{equation}

   \begin{equation}
 	  c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, \mathrm{d}s \: | \: X]  + E[\epsilon |\mathbf{X}]
   \end{equation}

   \begin{equation}
      c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,\mathrm{d}s
   \end{equation}

@@

    \begin{equation}
    	\int \beta(s)X(s) \,\mathrm{d}t \ = \sum_{k=1}^{K} c_{k} \int B_{k}(t)X_{i}(t)\,\mathrm{d}t =: \sum_{k=1}^{K} x_{ik} c_{k} 
    \end{equation}

@@

    \begin{equation}
    	f_2 = 1.5^{\frac{-0.5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0.5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0.5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0.5(t-0.8)^2}{0.03^2}}
    \end{equation}
